Correlation Clustering with Dynamic Super-Nodes (DySNCC)

### 2014-10-10 paper/egpaper_for_review.tex
minor changes

Nunez-Iglesias \etal describe the multicut as
\say{one-shot agglomeration of supervoxels} whose 
main drawback is the scalability \cite{nunez_iglesias_2013}.
To address scalability, supernodes can be useful.
To create supernodes, some edges will be contracted
and their nodes are merged into super-nodes.
Doing so, we can reduce  the graph 
to a reasonable size, such that we can find
global optimal multicut solutions within reasonable time.
%
Any edge which is contracted is lost.
If such an edge is cut in the global optimal solution, we cannot 
find this global optimal solutions.
Therefore we avoid fixed decisions and use a
dynamic energy aware contraction scheme.
%
Different edge contractions lead to different super-node graphs.
A trivial approach is the following.
Create different super-node graphs, optimize them with multicuts,
and take the result which leads to the lowest energy
on the unmodified initial graph.
% 
Doing so, we throw away all results which do not have the lowest energy.
Within this work we propose a framework which 
combine multiple \emph{proposal} super-node graphs
without any premature irreversible decisions.
Furthermore, multiple super-node graphs are combined such
that the information form all of them is used.
\todo[inline]{\emph{proposal} super-node graphs sounds shitty}

@@

\paragraph{Fully Connected Graph:}
\begin{center}
    \begin{eqnarray}
        y^*   & = & \argmin_{y} \sum_{ i<j \in V } w_{ij} \cdot y_{ij} \\
        s.t.: &  & x_{ij} + x_{jk} < x_{i,k} \quad \forall i, j, k   \nonumber
    \end{eqnarray}
\end{center}

@@

The multicut objective has been used for
\begin{inparaenum}[(i)]
    \item partitioning a superpixel region adjacency graph~\cite{andres_2011_iccv,kroeger_2012_eccv}
    \item with optional long range repulsive edges~\cite{andres_2013_emmcvpr}.
    \item Alush and Globerger showed how to average multiple segmentations with the multicut objective~\cite{alush_2012_pami}.
    \item Multicuts can also be used for interactive segmentation~\cite{bagon_2011_arxiv},
    \item for co-segmentation~\cite{glassner_2011_cvpr}
    \item and to cluster fully connected graphs~\cite{???}.
\end{inparaenum}

>>>>

Given an edge weighted graph, positive weights (\emph{attractive})
encourage the adjacent nodes to be in the same 
connected component, while negative weights (\emph{repulsive}) encourage
the nodes to stay in different connect components.
Therefore the sign of the weights encodes if two
nodes should be merged or not and the magnitude of the weights encodes
the certainty of this desire.
The objective of correlation clustering / multicuts
is finding the cut with a minimal sum of cut edge weights.
The number of connected components / clusters is discovered
from the weights ( rewrite?!?).
Correlation clustering / the multicut is NP-hard \cite{???}.
%
Despite the NP-hardness, correlation clustering has been 
successfully used for
\begin{inparaenum}[(i)]
    \item partitioning a superpixel region adjacency graph~\cite{andres_2011_iccv,kroeger_2012_eccv}
    \item with optional long range repulsive edges~\cite{andres_2013_emmcvpr}.
    \item Alush and Globerger showed how to average multiple segmentations with the multicut objective~\cite{alush_2012_pami}.
    \item Multicuts can also be used for interactive segmentation~\cite{bagon_2011_arxiv},
    \item for co-segmentation~\cite{glassner_2011_cvpr}
    \item and to cluster fully connected graphs~\cite{???}.
\end{inparaenum}

\todo[inline]{WHY WE NEED THIS NEW SOLVER?}

Nunez-Iglesias \etal describe the multicut as
\say{one-shot agglomeration of supervoxels} whose 
main drawback is the scalability \cite{nunez_iglesias_2013}.

\todo[inline]{BETTER MOTIVATE SUPERNODES}

To address scalability, supernodes can be useful.
To create supernodes, some edges will be contracted
and their nodes are merged into super-nodes.
Doing so, we can reduce  the graph 
to a reasonable size, such that we can find
global optimal multicut solutions within reasonable time.
%
Any edge which is contracted is lost.
If such an edge is cut in the global optimal solution, we cannot 
find this global optimal solutions.
Therefore we avoid fixed decisions and use a
dynamic energy aware contraction scheme.
%
Different edge contractions lead to different super-node graphs.
A trivial approach is the following.
Create different super-node graphs, optimize them with multicuts,
and take the result which leads to the lowest energy
on the unmodified initial graph.
% 
Doing so, we throw away all results which do not have the lowest energy.
Within this work we propose a framework which 
combine multiple \emph{proposal} super-node graphs
without any premature irreversible decisions.
Furthermore, multiple super-node graphs are combined such
that the information form all of them is used.
\todo[inline]{\emph{proposal} super-node graphs sounds shitty}
%
The proposed algorithm can be interpreted as a fusion moves
algorithm for correlation clustering / multicut objective.
We generate cheap and versatile proposals
and \emph{fuse} them with the current best solution with the
guarantee that this cannot increase the energy.

@@

\paragraph{Fully Connected Graph:}
\begin{center}
    \begin{eqnarray}
        y^*   & = & \argmin_{y} \sum_{ i<j \in V } w_{ij} \cdot y_{ij} \\
        s.t.: &  & y_{ij} + y_{jk} < y_{i,k} \quad \forall i, j, k   \nonumber
    \end{eqnarray}
\end{center}

@@
